\textbf{Designing a Virtual Security Layer for Cloud Content}

### 2015-10-08 tex/paper.tex
Added section about REST

What is needed
* Security layers
* Views
* Virtual file structure
* Versioning of content
* Multi project support
* Auth and audit logs
* Users

\section{Model}
\subsection{Entities}
%\subsubsection*{View} for not having section numbers
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{Entity Relationships}
    \label{fig:relation}
\end{figure}

\subsubsection{View}
A view is a group of files which can be changed independently of the view's parent.
A view can have subviews which are either automatically dependant on its parent and 
updated when the parent is updated or optionally updated or forked from its parent 
once their content diverge.

\subsubsection{Project}
A project is just a name for the view which is a root of a tree of views.
The system can contain several projects and their trees are completely disjoint.

@@

\subsubsection{Content}
Content is an asset contained in a view, it is a virtual file.
It could be described as a link between the view and the real file. 
It can be for example an image, video or binary blob combined with meta-data.

\subsubsection{User}
A user is the structure that handles people who has been granted access to the system.
Access to the system is handled by a separate service, like LDAP.

\section{Copy-on-Write}

@@

\section{Resulting system}
\subsection{REST Endpoints}
For the frontend to communicate with the backend REST is used, the following endpoints were configured:

@@

  \item projects/\{id\}/views
      \subitem GET - list all views in a specific project
      \subitem POST - create new view in a specific project 
  \item projects/\{id\}/views/\{id\}
      \subitem GET - get specific view in a specific project
      \subitem PUT - update existing view
      \subitem DELETE - delete existing view
  \item projects/\{id\}/views/\{id\}/content
      \subitem GET - list all content in a specific view
      \subitem POST - create new content in a specific view 
  \item projects/\{id\}/views/\{id\}/content/\{id\}
      \subitem GET - get specific content in a specific view
      \subitem PUT - update existing content in a specific view
      \subitem DELETE - delete existing content in a specific view
\end{itemize}

>>>>

What is needed
* Security layers
* Views
* Virtual file structure
* Versioning of content
* Multi project support
* Auth and audit logs
* Users
\newpage 
\section{Model}
\newpage 
\subsection{Entities}
%\subsubsection*{View} for not having section numbers
\begin{figure}[htp] \centering{
    \includegraphics[scale=0.8]{relation.pdf}}
    \caption{Entity Relationships}
    \label{fig:relation}
\end{figure}

\subsubsection{Content}
Content is an asset contained in a project and/or view, it is a form of virtual file.
It could be described as a link between the view or project and the real file. 
    The content can be for example an image, video or binary blob, combined with meta-data.

\subsubsection{Project}
A project is what is created to contain all content related to a real project. Files can be changed within a project and 
the system can contain several projects and their virtual content are completely disjoint.

\subsubsection{View}
A view is a subset of content, in a project, from the state which they were in when the view was created. A project can 
contain many views. A view can have content which either is automatically dependant on its parent project and updated 
when the parent is updated or stay in the state which it was in when the view was created. This results in that the content 
within a view can not be updated independently from its project.

\subsubsection{Folder}
A folder is a virtual folder within the projects which contains content.

@@

\subsubsection{User}
A user is the structure that handles people who have been granted access to the system.
Access to the system is handled by a separate service, like LDAP.

\newpage 
\section{Copy-on-Write}

@@

\section{Resulting system}
\subsection{Persistent storage}
\subsubsection{MongoDB}

\subsection{API}
REST was chosen as the BSON format which is used in MongoDB is almost identical ~\cite{BSON} to the standardised JSON 
format which is used by RESTful services~\cite{JSON}.

\subsubsection{REST Endpoints}
For the frontend to communicate with the backend REST is used, the following endpoints were configured:

@@

  \item projects/\{id\}/views
      \subitem GET - list all views in a specific project
      \subitem POST - create new view in a specific project 
  \item projects/\{id\}/views/\{id\}
      \subitem GET - get specific view in a specific project
      \subitem PUT - update existing view
      \subitem DELETE - delete existing view
  \item projects/\{id\}/views/\{id\}/content
      \subitem GET - list all content in a specific view
      \subitem POST - create new content in a specific view 
  \item projects/\{id\}/views/\{id\}/content/\{id\}
      \subitem GET - get specific content in a specific view
      \subitem PUT - update existing content in a specific view
      \subitem DELETE - delete existing content in a specific view

  \item projects/\{id\}/folders
      \subitem GET - list all folders in a specific project
      \subitem POST - create new folder in a specific project 
  \item projects/\{id\}/folder/\{id\}
      \subitem GET - get specific folder in a specific project
      \subitem PUT - update existing folder
      \subitem DELETE - delete existing folder
  \item projects/\{id\}/folder/\{id\}/content
      \subitem GET - list all content in a specific folder
      \subitem POST - create new content in a specific folder 
  \item projects/\{id\}/folder/\{id\}/content/\{id\}
      \subitem GET - get specific content in a specific folder
      \subitem PUT - update existing content in a specific folder
      \subitem DELETE - delete existing content in a specific folder
\end{itemize}
